Specialisation in food webs scales with species richness but not with latitude

### 2015-08-24 manuscript/AC-reply-to-referees.tex

  \begin{refquote}

    Please strictly follow the author guidelines with regard to layout (for
    example how to cite studies in the text).

  \end{refquote}

  \textbf{R:} We have changed all refences to the Vancouver style and have added sections for author contributions, conflicts of interest, and funding.
  [[Check the in-text citations match published papers]]

@@

    \smallskip

    Please justify why you use the proportion of species within a trophic
    level and not the absolute number of species per trophic level; at a first
    glance, this would be more intuitive for me given the focus of the study
    on scaling relationships with species richness.

  \end{refquote}

  \textbf{R:} Following the Referee's suggestion, we have moved our analysis of scaling relationships by trophic levels to the supplemental information. [[Need to address the rest of this.]]

### 2015-08-24 manuscript/latitudepaper.tex
All but one of the AE's points has been addressed

@@

  We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
  the manuscript.
  This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
  graduate scholarship (to ARC).

\newpage
\bibliographystyle{jae}%Compile with jae.bst style file
\bibliography{noISN}% your .bib file(s)

>>>>

\section*{Competing interestes}

  We have no competing interests.

\section*{Authors' contributions}

  ARC, DBS, and TNR designed the study, ARC collected
  published data, performed the analyses, and drafted the 
  article. DBS and TNR substantially revised the article;
  all authors approved the final version.

@@

  We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
  the manuscript.

\section*{Funding}
  This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
  graduate scholarship (to ARC).

\newpage
\bibliographystyle{vancouver}%Compile with vancouver.bst style file
\bibliography{noISN}% your .bib file(s)
